### 2019-08-01 Thesis/pages/design.tex
Changes; - More progress in the design section

@@

\subsubsection{Quality control}
\textbf{TODO}

>>>>

\textbf{TODO: } Explain why the attacks are designed like this. Use heatmap study as justification as why the ends are prioritised.

@@

\subsubsection{Quality control}
As the previous experiment, participants will be sourced from MTurk. Therefore, again, quality control is and aspect that requires consideration. As with the previous study, initially screened native speakers will be used. The same process will be performed to recruit suitable workers. Two metrics will be used to detect invalid results. Audio button clicks and overall time taken.

Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID}. If there are rounds without button clicks, this is a sign of non-attentive users. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

Overall time taken is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time it can be used as another detection for invalid responses. Anything below a certain threshold will be discarded.
